UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-19 paper/paper.tex
updates

\section{Methodology and setup description}

@@

Machines in Google Cluster Trace dataset do not have any pricing data attached. For further evaluation purposes, we have to assign example pricing schemes to each virtual machine.

Total number of machines: 12583
0.5 and 0.5,0.25 = 10595 = 84.2\% = heavy
rest = 1988 = 15.8\% = medium

@@

>>>>

\section{Methodology and setup description}
Tools:
Apache Spark, Google Data Trace, Workstation

@@

Machines in Google Cluster Trace dataset do not have any pricing data attached. For further evaluation purposes, we have to assign example pricing schemes to each virtual machine. 
Assumption: we take ip(medium, heavy) and assign heavy scheme to cpu and mem of platform B. The rest is medium.

Measurement period = 29 days
Total number of machines: 12583
0.5 and 0.5,0.25 = 10595 = 84.2\% = heavy
rest = 1988 = 15.8\% = medium

@@

Pricing: m2.4xlarge
m_medium = upfront : 2604, perhour : 0.52 
m_heavy = upfront : 3156, perhour : 0.272

\myparagraph{Cluster statistics}
\begin{center}
    \begin{tabular}{| l | l | l |}
    \hline
    Indicator & Scheme 1 & Scheme 2 \\
    \hline
    Total cost & \$8 177 048 & \$5 637 418 \\
    \hline
    KDI & +3 215 231 & +5 431 137 \\
    \hline
    Total CPU & 15972217.38 & 15972217.38 \\
    \hline
    Total Memory & 30676363.36 & 30676363.36 \\
    \hline
    Number of tasks & 1234716525 & 1234716525 \\
    \hline
    \end{tabular}
\end{center}

\section{Recognize inefficiencies and suggest changes}

The report will filter all machines that reported non-optimal - negative distance from intersection point - configuration during measurement period (29 days).

\myparagraph{Scheme 1}
Number of machines to tune: 932
CPU capacity to accommodate: 1 320 781.36
Memory capacity to accommodate: 4 286 742.06
Number of tasks to execute: 118869614
Cost of running non-optimal machines: \$657 200
Total uptime: 648519
cost per hour = \$1.01338588383687
Cost per task =  \$657 200 / 118869614 = \$0.00552874681666

\myparagraph{Scheme 2}
Number of machines to tune: 937
CPU capacity to accommodate: 1 327 202.18
Memory capacity to accommodate: 4 303 983.31
Number of tasks to execute: 119367988
Cost of running non-optimal machines: \$532 840.76
Total uptime: 651899

Avg cpu usage per machine = 15972217.38/12583 = 1269.35/29 = 43.77
Avg mem usage per machine = 30676363.36/12583 = 2437.92/29 = 84.06
Avg tasks number per machine = 1234716525/12583 = 98125.77/29 = 3383.65

\myparagraph{Squeeze-them-in suggestion strategy}

\myparagraph{Scheme 1}
total spare cpu = 3 697 171.44
total spare mem = 6 685 407.83
total distance: +3 500 037
total uptime = 8056601
cost per hour = \$7 519 848 / 8056601 = 0.93337723935938
new total cost = \$8 177 048 - \$657 200 = \$7 519 848
new cost per task = \$7 519 848 / 1234716525 = 0.00609034369245

new averages 
cpu per machine = 15972217.38/11651 = 1370.88 / 29 = 47.27
Avg mem usage per machine = 30676363.36/11651 = 2632.94/29 = 90.79
Avg tasks number per machine = 1234716525/11651 = 105975.15/29 = 3654.31

\myparagraph{Scheme 2}
total spare cpu = 3 694 240.56 
total spare mem = 6 682 956.59
total distance: +3 501 467
total uptime = 8053221

\myparagraph{New capacity configuration suggestion}

Input

c_name = cc2.8xlarge
c_light = "upfront" : "1762", "perhour" : "0.904" 
c_medium =  "upfront" : "4146", "perhour" : "0.54" 
c_heavy =  "upfront" : "5000", "perhour" : "0.361"

# values for size: m2.4xlarge region: us-east
# 1 year reservation
m_name = 'm2.4xlarge'
m_light =  "upfront" : "1088", "perhour" : "0.676" 
m_medium =  "upfront" : "2604", "perhour" : "0.52" 
m_heavy =  "upfront" : "3156", "perhour" : "0.272"

vm1 = Entity(c_name, c_light, c_medium, c_heavy)
vm2 = Entity(m_name, m_light, m_medium, m_heavy)

>>> calc_options(uptime, vm2, 29)
(1597, 3727, 972, 567 273.49, 998 186.23, 410 041.68)
>>> calc_options(uptime, vm1, 29)
(1397, 1720, 972, 770 417.58, 876 376.34, 604 274.61)
